Optical Detection of Paramagnetic Defects in a CVD-grown Diamond

### 2021-02-23 Mes papiers/CR-CVD/Reviewer_answer.tex

\documentclass{article}
\usepackage{physics}
\usepackage[]{quoting}

\begin{document}

\section*{Summary of the changes}

We would first like to thank the referees for the time they spent reviewing of our manuscripts.

Both referees found our work interesting for the field and our experimental results to be solid. They however pointed to several points lacking from the original manuscripts, in particular in regard to specifications of the sample and the defects we study, and the possibility to quantitatively measure the concentration of the new defects that we found.

We agree with these remarks and have amended the manuscript in consequence to the best of our abilities.

\section*{Referee 1}
\subsection*{Referee 1 report}

\begin{quote}
In this paper, Pellet-Mary et al. carry out a systematic investigation of paramagnetic defects other than the nitrogen vacancy center in cvd grown diamond. Utilizing NV center fluorescence in the same sample and sweeping an external magnetic field in the [100] direction, paramagnetic defects are identified as fluorescence dips at certain fields when the Zeeman split energy levels overlap. The identification and understanding of paramagnetic defects is important as they might serve as sources of decoherence in the diamond sample, and thus the present article yields important information. I have the following questions and comments before I can recommend publication.

1) On page 1, the authors briefly refer to Fig. 1 illustrating the different types of defects detected here. I believe the readers would appreciate if the defects with their respective properties could be introduced briefly already here.

2) The authors describe the sample fabrication on page 2 and it is mentioned earlier that they address a high density NV spin ensemble. However, I believe many readers would be interested in the nitrogen and nitrogen vacancy concentration obtained in the sample. The N (or P1 center) concentration is mentioned later on page 3, but this should presented coherently on the sample description?

3) On page 2, the paragraph starting with "Most experimental studies have been carried out...." It is not exactly clear which kind or type of experiments the authors refer to.

4) On page 2, the authors write "...T*2 was not degraded after annealing, yet the NV density was large enough to enable concentration dependent longitudinal relaxation [15, 17]." Thus, is the sample here the same as the one in Refs. [16, 17]?

5) On page 3, the text explaining the model illustrated in Fig. 4: in my opinion, the authors could add some information on the model. What is the symmetry of the defects and their orientation?

6) The spectra in Fig. 3 are fitted with Gaussian functions, though resonances should have a Lorentzian lineshape. Is there a particular reason for the choice?

7) The detection of the three electron spin-1 species in their sample is convincing. Using their method, would it be possible also to estimate the species concentration and eventually the spin dynamics? I discussion of this would be appreciated.

8) A more thorough discussion about the applied growth conditions and the occurrence of the observed defects would be useful? Does the concentration of the mentioned complexes (NVH, VH, VH2) strongly change as a function of e.g. temperature?

Minor comments:

- On page 2, the reference to Fig. 1-b) has a typo.

- The magnetic field axis in Figs. 3 and 4 have no units.

- The legend in Fig. 4 should read ‘13C-NV’ instead of 13C as explained in the text.
\end{quote}

\subsection*{Our answer}
Here is our answer to the points raised by Referee 1 :
\begin{enumerate}
\item We have added a short description of the three relevant defects of this study when describing Fig.1
\item We have added the concentration of NV and N in the description of the sample.
\item We have reformulated the sentence to make clear that we mention other cross-relaxation studies based on NV centers.
\item We have rewritten the paragraph to make it clear that this is indeed the same sample.
\item We have added information on the symmetry of the different defects with respect to the [100] axis to justify that we only take into account two transitions per defect in our model (except for the 13C-NV defect which is described in the supplementary material)
\item We added a discussion on the Gaussian vs Lorentzian line-shape in the description of fig.3. Given that the approximate shorter distance between our spins is more than 10 nm, the coupling strength between our spins would be less than 100 KHz. The width of the lines in fig.3 is therefore essentially due to the inhomogeneous Gaussian broadening of the ensemble of spins.
\item We added a paragraph at the end of the manuscript where we give a tentative estimate of the VH- and WAR1 concentration based on our measurement.
\item La c'est plus tendu de répondre. Alex ?
\end{enumerate}

We corrected the typos and missing information pointed in the minor comments and thank Referee 1 for their observations.

\section*{Referee 2}
\subsection*{Referee 2 report}
\begin{quote}
Pellet-Mary et al. report an experimental study on detecting paramagnetic defects in CVD-grown diamond by performing optical scans. From the optical detection of NV’s photoluminescence (PL) in varying external magnetic field, the authors identify two spin-1 defects, namely VH- and WAR1 in diamond based on cross-relaxations between NV centers and these defects. The authors further attribute a broad dip signal in PL to the interaction between bare NV and strongly coupled NV-C13 pairs.

In general, I find this work interesting and the experiment results are solid. The manuscript is also clearly written. However, I think there are several issues that should be addressed or clarified before further assessment. Specifically, to make the arguments more solid, the following points should be addressed.
Issues and questions:

1. In plotting the subtracted normalized PL curve, the authors used a 4th-order polynomial to fit the PL curve. Can the authors explain how they choose the order of the fitting function? Specifically, a higher order of polynomial might hide the spectral bumps that we are interested in and a lower order might result to a worse signal-to-noise ratio.

2. Similar question as above: would it be possible to theoretically calculate the PL drop vs B field using the transverse component of the magnetic field that results to the NV state mixing?

3. The zero-field-splittings (ZFS) of two defects were extracted from the position of two spectral bumps (one at 56 G another at 122 G). Could other information related with these defects be extracted from the salient features in the PL curve? For example, the depth (signal contrast) of the two dips could be related with defect concentrations and the width might have a connection with inhomogeneities in interactions between NVs and the defects.

4. The authors claimed that the signal of VH- and WAR1 defects was not observed in several HPHT samples. Would it be attributed to the difference (if any) between CVD-grown and HPHT samples in the irradiation and annealing process? For clarification, it might better to list the details of NV creation process for the HPHT samples.

5. Could the authors give some brief explanation that why the VH- and WAR1 defects only observed in CVD-grown samples (from the view of chemistry/material science)?

6. What’s the concentration of 13C in the CVD sample used in the study? Comparing it with the NV concentration (about 4.6ppm), what will be the probability that a NV center would have a strongly coupled first-shell C13? Would the resonant condition be the same for 13C-NV pairs beyond first shell interactions? These questions should be better clarified in the manuscript.

7. Could the authors briefly mention whether it’s possible that the technique could be extended to detect defects that have ZFS that are very different from NV center’s?

8. What is the quantization axis of the observed defects with respect to the [100] axis? Would the picture in Fig.4 still hold if one considers possible state mixings?

Some minor issues:

1. The legend label of 13C in Fig.4 (also Fig.1 in SI) is misleading. I would suggest label it with ‘NV- 13C’ instead of ‘13C’.

2. As mentioned before, I would suggest adding more information on the CVD sample such as 13C abundancy as well as estimation of defect concentrations, if possible.
\end{quote}
\subsection*{Our answer}
Here is our answer to the points raised by Referee 1 :
\begin{enumerate}
\item We have added a discussion of the 4th order polynomial in the description of fig.3, Referee 2 was mostly right on their assumption regarding the order of the polynomial. (although we have not really seen hiding of the spectral bumps even for higher order polynomial)
\item In the same section we explain that we tried to find a numerical solution for the overall decrease of PL with the magnetic field, but the solutions we found were not in agreement with our experimental data. (the decrease in our data seem too linear compared to the predicted quadratic profile of the numerical simulations)
\item We added a discussion regarding this point (similar to question 7 of Referee 1) at the end of the manuscript. It is in fact possible to extract an estimate of the concentrations with the area of the peaks (which is probably more relevant than the amplitude of the peaks in this case), but the width of the peak is mostly due to inhomogeneous broadening and not to interactions.
\item On a pas les infos pour les adamas, je sais pas si on peut en avoir pour les sumitumo ?
\item Demander à Alex. Je pense qu'il faut juste justifier le fait qu'il y ait plus d'hydrogène dans les CVD que dans les HPHT.
\item We have added a discussion of the concentration of 13C-NV pairs in the last paragraph when quantifying the concentration of our species. As for the beyond fist-shell 13C we have clarified in the 13C section that any 13C further away than the first-shell would have an hyper-fine bonding of less than 15 MHz, making its contribution almost indistinguishable from the inhomogeneous broadening due to the ambiant spin bath.
\item We added on page 3 a clarification that scans in the [100] direction cannot be used to detect spins with ZFS too different from the NV centers, due to the transverse field depolarization of NV centers for high field values.
\item The quantization axes for the $S_z$ operator of NV, VH and WAR1 in fig.4 were taken to be one of the four $\langle 111 \rangle$ direction, which are all equivalent when the magnetic field is in the [100] direction. Although this is not clearly visible, fig.4 does take into account state mixing due to the transverse field, by diagonalizing the Hamiltonian with both the longitudinal and transverse contribution of the magnetic field. 
\end{enumerate}

As for the minor comments, we changed the label and added more information on the CVD sample when describing it, and a section on the different defects concentration. We thank Referee 2 for their observations.

\end{document}

### 2021-02-23 Mes papiers/CR-CVD/CVD_para.tex
tutu

\documentclass[9pt,twocolumn,twoside]{osajnl}
%% Please use 11pt if submitting to AOP
% \documentclass[11pt,twocolumn,twoside]{osajnl}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{natbib}
\usepackage{physics}

\journal{optica} % Choose journal (ao, aop, josaa, josab, ol, optica, pr)

% See template introduction for guidance on setting shortarticle option
\setboolean{shortarticle}{true}
% true = letter / tutorial
% false = research / review article
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

% (depending on journal).

\title{Optical detection of paramagnetic defects in a CVD-grown diamond using Nitrogen-Vacancy centers}

\author[1]{C. Pellet-Mary}
\author[1]{P. Huillery}
\author[1]{M. Perdriat}
\author[2]{A. Tallaire}
\author[1]{G. H\'etet}

\affil[1]{Laboratoire de Physique de l'Ecole normale sup\'erieure, ENS, Universit\'e PSL, CNRS, Sorbonne Universit\'e, Universit\'e Paris-Diderot, Sorbonne Paris Cit\'e, Paris, France.}

\affil[*]{Corresponding author: gabriel.hetet@ens.fr}

%% To be edited by editor
% \dates{Compiled \today}

%\ociscodes{(140.3490) Lasers, distributed feedback; (060.2420) Fibers, polarization-maintaining;(060.3735) Fiber Bragg gratings.}

%% To be edited by editor
% \doi{\url{http://dx.doi.org/10.1364/XX.XX.XXXXXX}}

\begin{abstract}
The spins of Nitrogen Vacancy centers in Chemical Vapor Deposition (CVD) grown diamonds form ideal probes of magnetic fields and temperature, as well as ideal qu-bits for quantum information processing. 
Studying and controlling the magnetic environment of NV centers in such high purity crystals is thus essential.
In this letter, we demonstrate optical detection of paramagnetic species in a CVD grown diamond, such as hydrogen-related complexes, by coupling them to NV centers.
%We also unravel the role played by double quantum processes at zero magnetic field in the NV relaxation. 
The resonant transfer of NV centers spin-polarization to the electronic spins of these defects induces a loss of the NV photoluminescence, generating conspicuous features in the NV photoluminesence. 
The resonant condition is tuned with high accuracy by scanning a magnetic field along the 100 crystal direction.
Our results offer prospects for more detailed studies of CVD grown processes as well as for coherent control of the spin of a novel class of paramagnetic species.
\end{abstract}

\setboolean{displaycopyright}{true}

\begin{document}

@@

\section{Introduction}
The electronic spin properties of the negatively charged nitrogen-vacancy (NV$^-$) center in diamond has given rise to a wealth of applications in nanoscale sensing and quantum information science. One major reason is that it can be optically polarized and read-out and features long coherence time even at ambient conditions. 
%The NV property can also then be employed to manipulate and to detect other dark spins that are interacting with it through dipole-dipole coupling, either inside or outside the diamond. 
In order to optimize the capabilities of the NV center, its magnetic environment must be controlled carefully. 
Synthetic growth of diamond crystal now reaches a level of control that makes pristine diamond crystals almost flawless, eliminating the source of magnetic noise from other nearby impurities. The standard growth technique works through Chemical Vapor Deposition (CVD) of carbon atoms from a methane gas in an ultra clean vacuum environment. It offers the possibility to work with 99.9\% purity as well as using 12C enriched methane, hence removing spin fluctuations fro 13C atoms. More results from CVD.

The control of the purity of the material is typically done using Electron-Paramagnetic-Resonance (EPR). 
EPR operates with a very high resolution and was instrumental for detecting many species in diamond (uni of Warwick's review).
It would also be ideal if the defects were detected in the same platform that is used to for nanoscale sensing and quantum information processing, namely confocal microscopy. 
This would offer the opportunity to polarize these defects using the NV center, dynamically decouple them from the NV evolution for enhanced AC magnetometry and even to use them as ancilla qubits.

 \begin{figure}[htbp]
\centering
\fbox{\includegraphics[width=\linewidth]{Fig1.eps}}
\caption{Schematics showing various paramagnetic defects in CVD grown diamonds polarized by a Nitrogen Vacancy center. Bottom right :  crystalline structure of the diamond.}
\label{fig1}
\end{figure}

@@

Here, we use confocal microscopy and a high-density NV ensembles in a CVD grown diamond to detect paramagnetic defects from CVD grown sample.
The detection was realized using cross-correlation studies through magnetic field scans. 
Cross-relaxation typically takes place when the electronic or nuclear spins of two atomic species exchange their polarization via resonant magnetic dipole-dipole interactions. 
If the spin of an NV center is polarized and coupled to an unpolarized spin B, it will lose part of its polarization at the expense of B and thus see a drop of its PL rate. 
Tuning the frequency of both spin transitions will thus result in a drop of the NV photoluminescence when that they are co-resonant, thus enabling detection of the spin state of B.

The hamiltonian that describes typical spin-1 defects in diamond under a magnetic field be written as 
\bea
\hat{H}=\hbar D S_z^2+\hbar \gamma_e\bm S \cdot \bm B
\eea
where $S$ is...
The first term describes dipole interactions amongst the two electrons of the spin-1 system. The second term describes the Zeeman interaction.
$D$ can vary significantly from one defect to another as it is sensitive to the local crystal field. It can then be used to find the structure of the defect in EPR measurements.
Also, hyperfine interactions can add zero-field splittings that can be observed under high resolution scans. 
The angle of the magnetic field can thus also be to bring defects into resonance.

Cross relaxation amongst closely-packed NV centers can take place at moderate magnetic fields \cite{van_oort_optically_1991, van_oort_cross-relaxation_1989, armstrong_nvnv_2010, jarmola_longitudinal_2015, akhmedzhanov_microwave-free_2017, akhmedzhanov_magnetometry_2019, holliday_optical_1989, choi_depolarization_2017}, thus far, other impurities generally require by scanning large magnetic fields (more than hundreds of gauss) along the 111 direction of diamond. 
This is generally required to probe paramagnetic impurities that have a small ZFS. 
Most of the measurements are done at the ESLAC/GLSAC. OORT, BUDKER, HOLLENBERG, BAJAJ, MANSON.
Similar cross relaxation phenomena were studied by measuring changes in the optical hole depth in the zero-phonon line and studying decay rates oin stimulated spin-echo and spin-locking signals ? (BUDKER).

This procedure was proven useful for detecting the spin of $^{13}C$ atoms and the substitutional nitrogen Vacancy center in diamonds in the past. Such measurements not only show detection of this dark spins but can also be used to polarize them (Polarisation of 13C at low fields : PINES, MERILES ?). 
To date however, most studies have however been carried out using crystals grown by the High-Pressure-High-Temperature (HPHT) process, where a poor control over the paramagnetic defect density is available. In CVD grown samples, the typical paramagnetic impurities that have been detected by EPR are hydrogen complex such as the NVH, VH, VH2, where the hydrogen comes from the methane in the reactor. Fig.  \ref{fig1} shows a schematics of the various paramagnetic defects in a CVD grown diamonds that can be coupled to the Nitrogen Vacancy center in our study.

\begin{figure}[ht]
\centering
\fbox{\includegraphics[width=\linewidth]{Carte_annotation}}
\caption{NV$^-$ photoluminescence as a function of a scanning magnetic field around the [100] crystalline directions with a fixed amplitude $|B|=115G$. The planes orthogonal to the [010],[001],[011], and [01$\bar 1$] directions are indicated by dashed lines.}
\label{map}
\end{figure}

Recent work in the doping processes has shown the possibility to reach NV centers concentrations in the 3 to 5 ppm range in CVD grown samples \cite{Edmonds, TALLAIRE2020421, MINDARAVA2020182}, without sacrificing the $T_2^*$ coherence time, opening a path towards detecting these hydrogen-related complexes using cross-relaxation with NV centers.
%Several impurities in CVD grown diamonds have been detected using Electron-Paramagnetic Resonance.  In order to purify diamond crystal and optimize their conduction and properties for prolonged qubit lifetimes. 
%Extensive work has been done in the past twenty years to detect and characterize the various  that appear in EPR. 
The sample we use in this study was grown using CVD with the addition of N$_2$0 in the methane phase. Then, high energy electron irradiation and in-situ annealing was realized in order to convert the nitrogen into NV centers. A concentration of 5 ppm of NV center was obtained.
It was shown that in this sample the $T_2^*$ was not degraded after annealing, and that the NV density was large enough to enable the observation of $T_1$ dependent concentration.  It is well-known that when the NV concentration increases above 1 ppm, the longitudinal decay of NV centers is degraded. 
Furthermore, it has been observed that cross-relaxation amongst closely pack NVs of different classes can be observed.
It was postulated that such a degradation of the $T_1$ time came from the coupling of NV centers to other NV related defects whose spin fluctuates.

To perform the cross-relaxation detection, we use a homebuilt confocal microscope that comprises a 1mW green laser, an objective with a numerical aperture of XX to focus the laser onto the sample as well as to collect the PL. The PL was filtered from the green laser using a dichroic mirror and a notch filter coupled to a multimode fiber and sent to avalanche photodiode. The magnetic field scans were realized using a C-shaped electromagnet driven by a XX generator.  We monitor the NV PL as the magnetic field is scanned.

Contrary the more commonly chosen $\langle 111 \rangle$ direction, we use magnetic field scans along the $\langle 100 \rangle$ direction. 
Looking at the diamond structure (bottom right in Fig.  \ref{fig1})-a), we see that in this direction, the four possible projections of the NV centers along the magnetic field are the same. This means that doing a B field scan along this direction will not make NV centers energies from different classes cross. At arbitrary angles, this can result is several lines that could mask cross-relaxation from other species. 
The down side of this choice of B field direction is that for large B field amplitudes, the transverse component of the B field makes the PL drop [], thus limiting the range of magnetic field amplitudes that can be employed.
In order to find the $\langle 100 \rangle$ direction we perform a preliminary angular scan of the magnetic field using a goniometer at a fix magnetic field amplitude.
Fig. \ref{map}-a)  shows the NV Photoluminescence as a function of magnetic field direction, referenced by azimuthal and polar angles $(\phi, \theta)$ in the above described CVD grown sample. The PL is seen to drop for particular values of the angle as anticipated.
%The symmetric pattern suggests that the diamond crystalline main directions play a role. Because of the anisotropy of the NV center, see \ref{Cristallo}, the NV PL drop can indeed be a signature of the crystal direction.
Such a drop of the PL along the crystal axis was already observed by many groups. LUKIN, HEMMER, BUDKER. JARMOLA. OORT
\cite{van_oort_optically_1991, van_oort_cross-relaxation_1989, armstrong_nvnv_2010, jarmola_longitudinal_2015, akhmedzhanov_microwave-free_2017, akhmedzhanov_magnetometry_2019, holliday_optical_1989, choi_depolarization_2017} and correspond to situation where NV centers cross. 
Using such a map enables to identify clearly the crystalline axis and, in particular, the central point on this map, the $\langle 100 \rangle$ direction.

The planes orthogonal to the [010],[001],[011], and [01$\bar 1$] directions are indicated by dashed lines and show the locus of the cross relaxation, with a smaller PL contrast. 
The width of the CR peak is compatible with the $T_2^*$ time at this B field values. The contrast is determined both by the fluctuating NV concentration and the polarized NVs.
Such a map can in itself be a useful tool in order to measure magnetic fields without microwave, as already pointed out in \cite{}.

To double check these interpretations, we run an electron spin resonances by fixing the magnetic field amplitude and by scanning the microwave frequency. 
Fig. \ref{map}-b) shows an ESR taken at the angle ... showing two degeneracies.
Fig. \ref{map}-b) shows an ESR taken at the angle .. .showing four degeneracies. This hints towards the 100 direction.

We now tune the magnetic field along the 100 direction and scan the magnetic field amplitude. 
Fig. \ref{scan} shows the PL as a function of magnetic field amplitude, along the $\langle 100 \rangle$ direction in the 15 G to 145 G range. 
Careful calibration of the magnetic field amplitude was realized using a microwave tone of known frequency ....
The angle was controlled to within XX. 
For these data, the averaging was done for XX days. 
Three features clearly appear in this spectrum : one broader feature at 20G, another one at 56 G and one last one at 122 G. 
We also note an overall drop of the PL, as a the result of state mixing in the optically excited state. 
We made attempts to fit this curve using the full 7 level model, but this only gave poor agreement with experimental data. Further work will be done in order to clarify this. 
In order to let the three salient features detach better from the spectrum, we thus resorted to a 4th order polynomial fit without the spectral bumps, and subtract it from the curve. The subtracted curve is displayed below.  The width and contrast of each peak can now be compared and the position of each peak can be determined with great accuracy.

\begin{figure}[htbp]
\centering
\fbox{\includegraphics[width=\linewidth]{Scans_fig4}}
\caption{Optical detection of cross-relaxations. \textbf{Top} NV$^-$ photoluminescence while scanning the magnetic field along the [100] crystalline direction (plain line) and polynomial fit to the fourth order (dashed line). \textbf{Bottom} Subtraction of the previous signal by the polynomial fit (circles), simulated CR magnetic field amplitude (dashed,vertical) and gaussian fits for the second and third dips (plain line)}
\label{scan}
\end{figure}

>>>>

\documentclass[9pt,twocolumn,twoside]{revtex4-1}

\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{natbib}
\usepackage{physics}

\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

\begin{document}
\title{Optical Detection of Paramagnetic Defects in a CVD-grown Diamond}

\author{C. Pellet-Mary$^{1}$}
\author{P. Huillery $^{1}$}
\author{M. Perdriat $^{1}$}
\author{A. Tallaire $^{2}$}
\author{G. H\'etet$^{1}$}

\affiliation{$^1$Laboratoire de Physique de l'Ecole normale sup\'erieure, ENS, Universit\'e PSL, CNRS, Sorbonne Universit\'e, Universit\'e Paris-Diderot, Sorbonne Paris Cit\'e, Paris, France.}
\affiliation{$^2$IRCP, Ecole Nationale Supérieure de Chimie de Paris, 11, rue Pierre et Marie Curie, 75005 Paris, France}

\begin{abstract}
The electronic spins of the nitrogen-vacancy centers (NV centers) in Chemical-Vapor-Deposition (CVD) grown diamonds form ideal probes of magnetic fields and temperature, as well as promising qu-bits for quantum information processing. 
Studying and controlling the magnetic environment of NV centers in such high purity crystals is thus essential for these applications.
We demonstrate optical detection of paramagnetic species, such as hydrogen-related complexes, in a CVD-grown diamond.
The resonant transfer of the NV centers' polarized electronic spins to the electronic spins of these species generates conspicuous features in the NV photoluminescence by employing magnetic field scans along the [100] crystal direction. 
Our results offer prospects for more detailed studies of CVD-grown processes as well as for coherent control of the spin of novel classes of hyper-polarized paramagnetic species.
\end{abstract}

@@

The electronic spin properties of the negatively charged nitrogen-vacancy (NV$^-$) center in diamond has given rise to a wealth of applications in nanoscale sensing \cite{Rondin_2014} and quantum information science  \cite{DOHERTY20131}.
One major reason is that it can be optically polarized and read-out and features long coherence time even at ambient conditions. 
%The NV property can also then be employed to manipulate and to detect other dark spins that are interacting with it through dipole-dipole coupling, either inside or outside the diamond. 
In order to optimize the capabilities of the NV center, its magnetic environment must be very well controlled. 
Synthetic growth of diamond crystals is now reaching a level of maturity that makes the most pristine diamond crystals almost flawless, thus eliminating the source of magnetic noise from other nearby impurities than the  NV sensor. The standard growth technique works through Chemical Vapor Deposition (CVD) of carbon atoms from a methane gas in an ultra-high vacuum environment. It offers the possibility to use crystals with 99.9\% purity, as well as using $^{12}$C enriched methane, hence removing spin fluctuations from $^{13}$C atoms and enhancing further the sensing capabilities of NV centers \cite{Achard}.

Electron-Paramagnetic-Resonance (EPR) spectroscopy is the method of choice for controlling the concentration of paramagnetic defects in materials.Thanks to their high resolution, EPR spectrometers are also essential tools for understanding the conformation of many defects that remain in
CVD-grown diamond materials \cite{newton_epr_2007, glover_hydrogen_2004, glover_hydrogen_2003}. However, compared to confocal microscopy, this equipment is rather bulky and less cost-effective. 
It would also be ideal if these defects were detected with the very same technology that is employed for nanoscale sensing \cite{Rondin_2014} and quantum information processing \cite{Yao}. 
It would indeed offer the opportunity to hyper-polarize these defects using the optically polarized NV center and to employ them as quantum bits at ambient conditions.

 \begin{figure}[htbp]
\centering
{\includegraphics[width=\linewidth]{Fig1}}
\caption{Schematics showing various paramagnetic defects in CVD-grown diamonds interacting with the electronic spin of a negatively charged nitrogen-vacancy center. \textbf{Bottom right}: Atomic positions in the diamond unit cell.}
\label{fig1}
\end{figure}

@@

Here, we use confocal laser microscopy to detect paramagnetic defects {\it via} the coupling to a high-density NV spin ensemble in a CVD-grown diamond.
Fig. \ref{fig1} shows a schematics of the various paramagnetic defects that have been coupled to the nitrogen-vacancy center and detected optically in our study. These defects are the VH$^-$ and WAR1 defects, two spin-1 defects with comparable zero field splitting to the NV$^-$ center \citep{glover_hydrogen_2004, cruddace2007magnetic}, as well as $^{13}$C $1/2$-nuclear spin, through hyper-fine coupling with a secondary NV$^-$ center.
The detection is realized by measuring the NV photoluminescence while performing magnetic field scans to resonantly enhance dipole-dipole interactions and observe cross-relaxations (CR).
Cross-relaxation typically takes place when the electronic or nuclear spins of two atomic species exchange their polarizations via resonant magnetic dipole-dipole interactions. 
If the spin of an NV center A is polarized and coupled to an unpolarized spin B with a much larger relaxation rate, it will lose part of its polarization at the expense of B and thus see a drop of its photoluminescence (PL) rate. 
Tuning the frequency of both spin transitions so that are co-resonant will result in a reduction of the PL of NV A, thus enabling detection of the spin energy of B.
%It can then be used to unambiguously identify the defect. The response to a change in the angle of a magnetic field can further be used to unravel the structure of the defect in EPR measurements.
%Hyperfine interactions can add zero-field splittings that can be observed under high resolution scans. 
%The angle of the magnetic field can thus also be to bring defects into resonance.

\begin{figure}[ht]
\centering
{\includegraphics[width=\linewidth]{Carte_annotation}}
\caption{a) NV$^-$ photoluminescence as a function of the magnetic field angle around the [100] crystalline direction, at a fixed amplitude $|\vec{B}|=115$G. The planes orthogonal to the [010], [001], [011], and [01$\bar 1$] directions are indicated by dashed lines. b) Left: Optically-detected-magnetic-resonance (ODMR) spectrum taken at the angular position $(\phi, \theta)=(3^\circ,3^\circ)$. Right: ODMR spectrum taken at the exact center of the map, {\it i.e.} the [100] direction.}
\label{map}
\end{figure}

The negatively charged nitrogen-vacancy center has a zero-field splitting $D=(2\pi) 2.87$ GHz in the ground state, related to the dipole-dipole interaction between the spin of the two unpaired electrons. One of the most important properties of the spin of the NV$^-$ center is that it can be optically polarized and read-out and features long relaxation time ($\approx $ms) even at ambient conditions, which can be used to detect other species via CR and even to polarize them. 
Many paramagnetic defects in diamond also carry a spin 1.
The zero-field splittings are in fact a fingerprint of the defect. To measure it, one can tune the angle and magnitude of an external magnetic field angle to cause cross-relaxation with the NV centers. The obtained CR position can then be used to trace back the zero-field splitting of the defect.
%Four possible directions of the NV axis in the crystalline diamond structure can then lead to CR amongst NV centers at moderate magnetic fields \cite{van_oort_optically_1991, van_oort_cross-relaxation_1989, armstrong_nvnv_2010, jarmola_longitudinal_2015, akhmedzhanov_microwave-free_2017, akhmedzhanov_magnetometry_2019, holliday_optical_1989, choi_depolarization_2017}.
%Detecting paramagnetic impurities using the NV center often requires large magnetic fields (> 500 G) along the diamond [111] direction. 
%This is generally required to probe impurities with an electronic spin 1/2 such as substitutional nitrogen, or the $^{13}$C nuclear spin.
%\cite{Epstein,Wang, armstrong_nvnv_2010, Hall, Wickenbrock}.
%Most of the measurements are done at the ESLAC/GLSAC. OORT, BUDKER, HOLLENBERG, BAJAJ, MANSON.
%Similar cross relaxation phenomena were studied by measuring changes in the optical hole depth in the zero-phonon line and studying decay rates oin stimulated spin-echo and spin-locking signals ? (BUDKER).
%This procedure was proven useful for detecting and understanding the spin of $^{13}C$ atoms and the substitutional nitrogen Vacancy center in diamonds in the past. 
%Such measurements not only show detection of dark spins but can also be used to polarize them (Polarisation of 13C at low fields : PINES, MERILES ?).

%In CVD grown samples, the typical paramagnetic impurities that have been detected by EPR are hydrogen complex such as the NVH, VH, VH2, where the hydrogen comes from the methane in the reactor. Fig.  \ref{fig1} shows a schematics of the various paramagnetic defects in a CVD grown diamonds that are coupled to the Nitrogen Vacancy center in our study.
Previous cross-relaxation studies with NV$^-$ centers have been mostly carried out using heavily doped crystals grown by the High-Pressure-High-Temperature (HPHT) process \citep{Epstein,Wang, armstrong_nvnv_2010, Hall, Wickenbrock, Alfasi}. 
Recent efforts in the doping processes have also made it possible to reach NV centers concentrations in the 3 to 5 ppm range in CVD grown samples \cite{Edmonds, TALLAIRE2020421, MINDARAVA2020182}, opening a path towards detecting other paramagnetic defects in CVD grown diamonds. 
%these hydrogen-related complexes using cross-relaxation with NV centers.%Several impurities in CVD grown diamonds have been detected using Electron-Paramagnetic Resonance.  In order to purify diamond crystal and optimize their conduction and properties for prolonged qubit lifetimes. 
%Extensive work has been done in the past twenty years to detect and characterize the various  that appear in EPR. 
The sample we use in this study  correspond to the pink irradiated sample in \cite{TALLAIRE2020421}. It was grown using CVD with the addition of 500ppm of N$_2$0 to the H2/CH4 (96/4) gas phase.
Then high energy (10MeV) electron irradiation at a fluence of $2\times18$ cm$^{-2}$ and at a temperature of 900 degrees celsius was realised, giving a final concentration of NV$^-$ of about 4.6~ppm for an initial concentration of nitrogen in the sample of about 25~ppm.
It was shown that in this sample the $T_2^*$ was not degraded after annealing, yet the NV density was large enough to enable concentration dependent longitudinal relaxation \cite{TALLAIRE2020421, jarmola_longitudinal_2015}.  
%It is well-known that when the NV concentration increases above 1 ppm, the longitudinal decay of NV centers is degraded. 
%Furthermore, it has been observed that cross-relaxation amongst closely pack NVs of different classes can be observed.
%It was postulated that such a degradation of the $T_1$ time came from the coupling of NV centers to other NV-related defects.

In this study, we use a homebuilt confocal microscope that comprises a 1mW green laser, an objective with a numerical aperture of 0.25 to focus the laser onto the sample as well as to collect the NV photoluminescence (PL). The PL was filtered from the green laser using a dichroic mirror and a notch filter. It was then coupled to a multimode fiber and detected by an avalanche photodiode. The magnetic field scans were realized using a C-shaped electromagnet driven by a current generator (HP 33120A).  We then monitor the NV PL synchronously with the changes in the magnetic field.
\begin{figure}[ht]
\centering
{\includegraphics[width=\linewidth]{Scans_fig4}}
\caption{Optical detection of cross-relaxations. {Top}: NV$^-$ photoluminescence counts as a function of the magnetic field amplitude along the [100] crystalline direction (plain line) and fourth-order polynomial fit (dashed line). {Bottom} Curve obtained by subtracting the polynomial fit to the above signal (circles). The simulated cross-relaxations positions are shown by the green dashed, vertical lines. Gaussian fits to the second and third dips are shown by plain orange lines.}
\label{scan}
\end{figure}
Contrary to the more commonly employed $[ 111 ]$ direction, we scan the magnetic field along the diamond $[100]$ crystalline direction. 
Looking at the diamond structure (bottom right in Fig.  \ref{fig1}), it can be noticed that, in this direction, the four possible projections of the NV centers (or any other $C_{3v}$ defect) along the magnetic field are identical. This means that a B field scan along this direction cannot make the transition energies of the different classes of NV centers cross. Under arbitrary angles, this could otherwise result in several low field PL features \cite{van_oort_optically_1991, akhmedzhanov_magnetometry_2019} that could mask cross-relaxation from other species and also reduce the CR contrast (see section 4 of the supplementary materials for data showing scans along the [111] direction). 
The downside of this choice of the [100] direction is that at large amplitudes, the transverse component of the magnetic field depolarizes all classes of NVs, thus limiting the magnetic field range that can be employed and therefore limiting this detection process to paramagnetic defects with zero-field splittings close to the NV center's one.

In order to identify the $[100]$ direction, we perform an angular scan of the magnetic field using a dual-axis goniometer (Thorlabs GNL20-Z8) that holds a permanent magnet at a fixed distance from the sample. 
Fig. \ref{map}-a) shows the NV photoluminescence as a function of magnetic field direction, referenced by azimuthal and polar angles $(\phi, \theta)$ with respect to the $[100]$ direction, using the above described CVD-grown sample. The PL is seen to drop for particular values of the magnet angular coordinates that correspond to specific crystalline axes.
Such a drop of the PL, also observed in
\cite{van_oort_optically_1991, van_oort_cross-relaxation_1989, jarmola_longitudinal_2015, akhmedzhanov_microwave-free_2017, akhmedzhanov_magnetometry_2019, holliday_optical_1989, choi_depolarization_2017}, correspond to situation where the transitions of NV centers become degenerate. 
The planes orthogonal to the [010], [001], [011], and [01$\bar 1$] directions are indicated by dashed lines and show the locus of the cross relaxation. These planes all cross on the [100] axis.
The origin of these sharp changes in the photoluminescence was attributed to cross relaxation between polarized NV centers and rapidly decaying NV centers, so called fluctuators \cite{choi_depolarization_2017}, the precise origin of the latter remains unknown.
The width of the CR features when the magnetic field crosses a plane perpendicularly was found to be compatible with the NV decoherence rate  ($\approx$ 6 MHz). The contrast is determined both by the fluctuating NV and polarized NV concentrations.
